### 2021-03-01 paper.Rmd
dot points

- Bases notation (Sherry)
- Display (Sherry)
- Choosing targets, inc pp indexes (Sherry)
- Geodesic interpolation (Ursula)
- Slices vs projections (Ursula)
- Transformations on projections (Ursula)

>>>>

- Bases notation (Sherry)

$d$-dimensional projection in $p$-dimensional space

Data: $X_{{n \times p}$, 
Basis: $A_{p \times d}$, commonly 1d or 2d projection, orthonormality, more displays in the next section - can display a matrix A, Link to geometry properties.
projection: $Y = X \cdot A$

- Display (Sherry)

[@Wickham2011-uz]

1D: `display_hist`: histogram
2D: `display_xy`, recent development `display_sage()` - will be detailed in the last section @Transformations on projections (Ursula)

- Choosing targets, inc pp indexes (Sherry)

grand tour, random, may miss interesting, take long to rotate to that specific angle, guided tour, along with projection pursuit, by generating target bases, interestingness

interesting, index function, $f: \mathbb{R}^{n \times d} \mapsto \mathbb{R}$, normality, theoretical result: [@Diaconis1984-mv], aslo peter huber projection pursuit

index: 
  - initial idea from Friedman, orthonormal function expansion (Do we need to review these old index contruction?)
  - holes, central mass, PDA, LDA
  - scagnostic indices
  - skewness & kurtosis index loperfido (moment)
  - chi-square @posse for detect spiral

- Geodesic interpolation (Ursula)
- Slices vs projections (Ursula)
- Transformations on projections (Ursula)
